Modelling Stochastic Time Delay for Regression

### 2021-02-14 documentation/article/article.tex
Title change
add images

\title{Modelling Stochastic Time Delay Structures for Regression}
\author{Aaron Pickering}
%\address{}
\email{aaron1rcl@gmail.com}
%\urladdr{} 
\date{\today}
\maketitle

@@

The following section demonstrates a simulated univariate example. Full code to reproduce the example can be found via \href{https://github.com/aaron1rcl/tvs_regression/}{TVS Regression on Github}.

Figure 2. shows the simulated time series.

@@

\begin{center}
\begin{figure}
\includegraphics[totalheight=6cm]{images/simulated_example.png}
\caption{Simulated Example Data}
\label{fig:verticalcell}
\end{figure}
\end{center}

A histogram of the actual distribution of $\mathcal{T}$ is shown in figure 3.

\begin{center}
\begin{figure}
\includegraphics[totalheight=6cm]{images/real_shifts.png}
\caption{Real Shift Distribution $\mathcal{T}$}
\label{fig:verticalcell}
\end{figure}
\end{center}

After fitting the model, we obtain the following results.
Figures 4 and 5 show the model fit (denoted TVS) and a comparison with standard OLS. Figures 6 and 7 fit convergence and scatterplot respectively.

\begin{center}
\begin{figure}
\includegraphics[totalheight=6cm]{images/tvs_fit.png}
\caption{TVS Model Fit $\mathcal{T}$}
\label{fig:verticalcell}
\end{figure}
\end{center}

>>>>

\title{Modelling Stochastic Time Delay for Regression}
\author{Aaron Pickering}
%\address{}
\email{aaron1rcl@gmail.com}
%\urladdr{} 
\date{\today}
\maketitle

@@

The following section demonstrates a simulated univariate example. Full code to reproduce the example can be found via \href{https://github.com/aaron1rcl/tvs_regression/}{TVS Regression on GitHub}.

Figure \ref{fig:simulated_example} shows the simulated time series.

@@

\begin{center}
\begin{figure}
\includegraphics[scale=0.5]{images/simulated_example.png}
\caption{Simulated Example Data}
\label{fig:simulated_example}
\end{figure}
\end{center}

A histogram of the actual distribution of $\mathcal{T}$ is shown in Figure \ref{fig:real_shifts}.

\begin{center}
\begin{figure}
\includegraphics[scale=0.5]{images/real_shifts.png}
\caption{Real Shift Distribution $\mathcal{T}$.}
\label{fig:real_shifts}
\end{figure}
\end{center}

After fitting the model, we obtain the following results. Figure \ref{fig:tvs_ols_fit} show the model fit (denoted TVS) and a comparison with standard OLS. Figure \ref{fig:tvs_errors} and Figure \ref{fig:convergence} show the errors distribution of the TVS fit and  convergence of the TVS model respectively.

\begin{center}
\begin{figure}
\includegraphics[scale=0.6]{images/tvs_fit.png} 
\includegraphics[scale=0.3]{images/ols_fit.png} 
\includegraphics[scale=0.3]{images/scatterplot.png} 
\caption{TVS vs OLS model fit.}
\label{fig:tvs_ols_fit}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\includegraphics[scale=0.5]{images/tvs_errors.png}
\caption{Errors...}
\label{fig:tvs_errors}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\includegraphics[scale=0.6]{images/convergence.png} 
\caption{Convergence ...}
\label{fig:convergence}
\end{figure}
\end{center}
